\papertitle

### 2021-03-11 source_separation/paper/paper.tex
added a few more changes I missed

	For example, consider an example target that has a continuous drone sound throughout and a melody playing above this drone. Without source separation, Orchidea would detect each note of the melody as a new onset and cut the target in time at each new note. However, this segmentation in time would also effect the drone, cutting it in time and forcing it to have a new onset each time the melody changes notes. The resulting orchestration would have multiple onsets for the drone, when really only one onset is needed at the beginning of the drone. When source separation is applied to this target, the drone and melody would be orchestrated separately. Therefore, the drone could be orchestrated by a single onset that lasts for the duration of the drone. At the same time, the melody could have as many new onsets as needed without affecting the drone. The orchestration would be greatly improved by removing the unnecessary onsets in the orchestration of the drone. This is the effect we hope to achieve through implementing source separation in computer-assisted orchestration.

@@

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Full target & 24.96 \\
				\hline
				NMF & 22.44 \\
				\hline
				Demucs & 25.11 \\
				\hline
				Open-Unmix & 24.48\\
				\hline
				TDCN & 26.44\\
				\hline
				TDCN++ & 24.38 \\
				\hline
				Ground truth & 24.19 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. "Full target" means no separation was performed.}
		\label{tab:distances}
	\end{table}

>>>>

	For example, consider an example target that has a continuous drone sound throughout and a melody playing above this drone. Without source separation, Orchidea would detect each note of the melody as a new onset and cut the target in time at each new note. However, this segmentation in time would also effect the drone, cutting it in time and forcing it to have a new onset each time the melody changes notes. The resulting orchestration would have multiple onsets for the drone, when really only one onset is needed at the beginning of the drone. When source separation is applied to this target, the drone and melody would be orchestrated separately. Therefore, the drone could be orchestrated by a single onset that lasts for the duration of the drone. At the same time, the melody could have as many new onsets as needed without affecting the drone. The orchestration would be greatly improved by removing the unnecessary onsets in the orchestration of the drone. This is the effect we achieve through implementing source separation in computer-assisted orchestration.

@@

		Suggestion: A block-diagram of the algo would be nice to have

@@

	\begin{table}[t]
		\begin{center}
			\begin{tabular}{|c|c|}
				\hline
				& Average distance \\
				\hline
				Full target & 24.96 \\
				\hline
				NMF & 22.44 \\
				\hline
				Demucs & 25.11 \\
				\hline
				Open-Unmix & 24.48\\
				\hline
				TDCN & 26.44\\
				\hline
				TDCN++ & 24.38 \\
				\hline
				Ground truth & 24.19 \\
				\hline
			\end{tabular}
		\end{center}
		\caption{Average across 300 targets showing the distance between target and orchestration for various methods. "Full target" means no separation was performed. Lower values are better.}
		\label{tab:distances}
	\end{table}
